### 2018-06-07 FrascatiPlot/Paper/NucleiB2.tex
first almost complete version of the master table.

\centering
\begin{tabularx}{\textwidth}{cccccccc}
%\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} \\ \hline
Mass number             & Nucleus                         & Composition                  & $B_{E}$ (MeV)   & Spin $J$ & charge rms radius (fm) &  harmonic oscillator width r (fm)  & Refs. \\ \hline
A = 2                           & d                                    & pn                                  &   2.224575 (9)     &     1       & 2.1413 $\pm$ 0.0025                 &  3.2                                 &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}      \\ \hline
\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) &      1/2   &  1.755  $\pm$ 0.086                   &                                                     &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) &        1/2    & 1.959 $\pm$  0.030                  &                                                       &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &                             &                 &                                                   &                                                      & \\ \hline
\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0         &  1.6755 $\pm$ 0.0028             &                                                       & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &                               &               &                                                    &                                                       &  \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &                               &               &                                                    &                                                       &\\
                                   & \hefourlambda              & pp$\Lambda$n              &                               &                &                                                    &                                                      &\\ \hline
\end{tabularx}
\caption{Properties of nuclei and hyper-nuclei. $B_{E}$ is the binding energy per nucleon in MeV and the radius is given in terms of the rms radius of the wavefunction. References are given in the last column.}
\label{tab:nucleusradii}
\end{sidewaystable}

>>>>

\centering
\begin{tabularx}{\textwidth}{XcccccXc}
%\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} \\ \hline
Mass \newline number & Nucleus                         & Composition                  & $B_{E}$ (MeV)   & Spin $J$ & (charge) rms \newline radius (fm) &  harmonic oscillator  \newline width r (fm)  & Refs. \\ \hline
A = 2                           & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}      \\ \hline
\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &             &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &              &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &            & \cite{Davis:2005mb,Nemura:1999qp} \\ \hline
\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &             & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8                       &                 & \cite{Davis:2005mb,Nemura:1999qp} \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1 (cf text in \cite{Nemura:1999qp})    &    4.2 -- 7.1                      &           &   \cite{Nemura:1999qp} \\
                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8                     &            & \cite{Davis:2005mb,Nemura:1999qp}\\ \hline
\end{tabularx}
\caption{Properties of nuclei and hyper-nuclei. $B_{E}$ is the binding energy per nucleon in MeV and the radius is given in terms of the rms radius of the wavefunction. References are given in the last column.}
\label{tab:nucleusradii}
\end{sidewaystable}
